brados: declarative, programmable object storage

### 2016-05-25 paper.tex
importnat
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

The reference count implementation that we describe does not use a typical
counter, but rather uses a tag-based interface in which each \emph{reference}
to an object is identified by a application-level tag. Each tag represents
one or more references allowing an idempotent property useful for application
that may replay reference count operations out of order. Otherwise the
semantics are straightforward: clients record references to an object, and
when the number of references drop to zero the object is removed.

The reference implementation in Ceph is 300 LOC written in C++. The version
written in Brados is shown in Listing~\ref{lst:rc}.

 Unlike the CORFU interface
that took advantage of a mapping between backend storage and collections, the
reference counting interface requires access to RADOS runtime facilities that
allow objects to be removed. This is modeled in Brados using the Bloom
\emph{channel} abstraction that is used to transmit facts between entities in
the system; we effectively send a message to the runtime with our removal
request.

>>>>

The reference count implementation that we describe does not use a typical
counter, but rather uses a tag-based interface in which each \emph{reference}
to an object is identified by a application-level tag. Each tag represents one
or more references supporting an idempotent property useful for applications
that may replay reference count operations out of order. Otherwise the
semantics are straightforward: clients record references to an object by
inserting a tag, and remove a reference by removing a tag. When the number of
references (i.e., tags) drop to zero the object is garbage collected.

The reference implementation in Ceph is 300 LOC written in C++. The version
written in Brados is shown in Listing~\ref{lst:rc}. Line 10 shows the
implementation of requesting a reference which is an idempotent merge of the
tag into the persistent \texttt{refs} collection.  Unlike the CORFU interface
that took highlighted how collections are unified with persistent storage, the
reference counting interface requires access to RADOS runtime facilities that
allow objects to be removed. This is modeled in Brados using the Bloom
\emph{channel} abstraction that is used to transmit facts between entities in
the system; we effectively send a message to the runtime with our removal
request. The \texttt{remove\_chn} channel may be populated with messages and
the RADOS runtime will processes these asynchronously.
